\documentclass[line,margin]{res}
\usepackage[none]{hyphenat}
\usepackage{textcomp}
\usepackage{hyperref} 

\begin{document}
\name{{\LARGE Vincent Le}}
\address{vincentl@vt.edu | (703) 992-5598 | \textbf{\href{https://github.com/vinnyoodles}{github.com/vinnyoodles}}}
\begin{resume}
	\vspace{-5mm}
	\section{EDUCATION}
		\textbf{Virginia Tech}, {\sl BS in Computer Science} GPA: 3.77\hfill May 2018\\Blacksburg, VA

	\section{EXPERIENCE}
		\textbf{Virginia Tech}, {\sl Undergraduate Research Assistant}\hfill Feb 2018 | Present\\Blacksburg, VA\\
		\begin{itemize} \itemsep 1pt
			\item Developed bioinformatics application for running and managing genome analysis.
			\item Implemented backend using flask and frontend with Bootstrap.
			\item Managed background jobs using celery and redis.
			\item Used Docker Compose to manage MongoDB, flask, redis and celery instances.
		\end{itemize}

		\textbf{Virginia Tech}, {\sl Undergraduate Teaching Assistant}\hfill Aug 2017 | Present\\Blacksburg, VA\\
		\begin{itemize} \itemsep 1pt
		\item Held office hours for the Data Structures and Algorithms course (CS 3114) for students
			  to get help on projects and homeworks.
		\item Topics covered were sorting, searching, graphs, trees, hashing, recurrence relations and algorithm analysis.
		\end{itemize}

		\textbf{Mixmax}, {\sl Software Engineering Intern}\hfill Aug 2016 | Aug 2017\\San Francisco, CA\\
		\begin{itemize} \itemsep 1pt
			\item Implemented CRUD functions for supporting multiple Mixmax teams and organizations.
			\item Added Chrome extension logic to embed email draft metadata into Gmail HTML.
			\item Rewrote Backbone frontend view code into React reusable components.
			\item Added Chrome extension logic to embed Mixmax into Salesforce HTML for integrating with its metadata.
			\item Implemented a background sync of Salesforce contact and lead data for autofilling metadata in forms and templates.
		\end{itemize}

	\section{PROJECTS}
	    \textbf{Collaboard}, {\sl Android, node.js, socket.io, MongoDB}\\ https://github.com/vinnyoodles/whiteboard\\
	    \begin{itemize} \itemsep 1pt
			\item Published an Android app with realtime whiteboarding and voice chat features.
			\item Wrote node.js server with WebSocket communication protocol using socket.io and deployed onto Heroku.
			\item Persisted canvas data with base64 encoding in MongoDB.
			\item Implemented audio communication by streaming bytes through WebSockets.
	    \end{itemize}
	    \textbf{mosaic-layout}, {\sl swift, xcode, UIKit}\\ 
	    https://github.com/vinnyoodles/mosaic-layout\\
	    iOS library implementation of a tile/mosaic based collection view, written with a protocol oriented design pattern.\\

	\begin{tabular}{@{}ll}
		\textbf{Programming Languages}: & Java, C, Javascript, Python   \\
		\textbf{Frameworks/Libraries}:  & node.js, backbone.js, React, Socket.io, MongoDB, Android \\
	\end{tabular}
\end{resume}
\end{document}
